### 2015-02-02 paper/conclusion.tex
experiment 1 take 2 results; +plotting switch; some paper updates including references
conclusion

\section{Conclusion}
The conclusion goes here.

>>>>

\section{Conclusion}
We studied the problem of route flow estimation from the perspective of a sensitivity analysis, using a structured noise model based off of communication network handoff algorithms. We presented our preliminary results on the effect of the structured noise on the recovery of route flow, and we plan to continue this analysis with more extensive trials. This work is in preparation for a full-scale run of the route flow estimation on cellular signaling data from AT\&T in the greater Los Angeles area. We additionally plan to investigate a sensitivity analysis for the dynamic route flow estimation problem, and we plan to use our handoff model to augment our prior on vehicle connectivity.

% Multiple cellpaths per route
